Illustrating Model Properties

### 2024-05-29 model.qmd
work on contra inv dep. on ipsi III

for t_stage in ["early", "late"]:
  for diagnosis in [{"II": True}, {lnl: False for lnl in ["I", "II", "III", "IV", "V"]}]:
    color = next(colors)
    scenario = Scenario(
      t_stages=[t_stage],
      diagnosis={
        "ipsi": {"max_llh": diagnosis},
        "contra": {"max_llh": {"II": True}},
      }
    )
    content.append(
      Histogram.from_hdf5(
        filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
        dataname=scenario.md5_hash("prevalences"),
        color=color,
        label="prediction"
      )
    )
    beta_post = BetaPosterior.from_hdf5(
      filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
      dataname=scenario.md5_hash("prevalences"),
      color=color,
    )
    beta_post.kwargs["label"] = f"data: {beta_post.num_success} of {beta_post.num_total}"
    content.append(beta_post)

>>>>

for t_stage in ["early", "late"]:
  for diagnosis in [{"III": True}, {lnl: False for lnl in ["I", "II", "III", "IV", "V"]}]:
    color = next(colors)
    scenario = Scenario(
      t_stages=[t_stage],
      midext=True,
      diagnosis={
        "ipsi": {"max_llh": diagnosis},
        "contra": {"max_llh": {"II": True}},
      }
    )
    content.append(
      Histogram.from_hdf5(
        filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
        dataname=scenario.md5_hash("prevalences"),
        color=color,
        label="prediction"
      )
    )
    beta_post = BetaPosterior.from_hdf5(
      filename=paths.model_dir / "full" / "prevalences_with_ipsi.hdf5",
      dataname=scenario.md5_hash("prevalences"),
      color=color,
    )
    beta_post.kwargs["label"] = f"data: {beta_post.num_success} of {beta_post.num_total}"
    content.append(beta_post)
